\section{Education}

In May 2011, Rafael Plaza became the first student in our university
to graduate with a thesis on a GPU-related topic.
For his Master's thesis titled Lattice-based algorithms for the computation of
Humber-Hermite number in Z, he implemented number-theoretical algorithms on the GPU.

Afterwards in 2012, PhD student César Fernández and M.Sc students Cristián Maureira,
Gabriel Zamora and Roberto Bonvallet used CUDA for their theses,
respectively in Computational Finances, Astrophysical Simulations,
Electromagnetic Signal Processing and Computational Fluid Dynamics.

This scenario was the reason to be able to achive the award of being a
NVIDIA CUDA Teaching Center~\footnote{\url{https://research.nvidia.com/content/cuda-teaching-centers-nala\#Chile}} during the years 2011 and 2012.
The NVIDIA CUDA Teaching Center project was in charge of Prof. Luis Salinas
and Roberto Bonvallet.

During that period,
the people involved decided to provide the UTFSM community
with different courses and seminars, being able to spread the HPC knowledge
to guvernamental divisions.

All the seminar had as a main goal to learn about the fundamentals in GPU related
to the High Performance Computing, following by real application,
helping to solve problems and generate projects and products into the
scientific society.

The courses were:

\begin{itemize}

    \item \textbf{High Performance Computing using GPU}
        \begin{itemize}
            \item Professor: Roberto Bonvallet, UTFSM.
            \item Date: Second Semester, 2010.
            \item Description: Computer Science Elective Course, UTFSM.
        \end{itemize}

    \item \textbf{High Performance Computing}
        \begin{itemize}
            \item Professor: Roberto Bonvallet and Cesar Fernandez, UTFSM.
            \item Date: Second Semester, 2011.
            \item Description: Computer Science Elective Course, UTFSM.
        \end{itemize}

    \item \textbf{CUDA Winter School Topics}
        \begin{itemize}
            \item Professor: Christopher Cooper, Boston University.
            \item Date: August 8th to September 2nd, 2011.
            \item Description: Seminar to all the UTFSM community.
        \end{itemize}

    \item \textbf{Introduction to GPU Computing using CUDA}
        \begin{itemize}
            \item Professor: Roberto Bonvallet, Cristian Maureira, Gabriel Zamora.
            \item Date: May 2012
            \item Description: Seminars for the Chilean Army Intelligence Division
                (Dirección de Inteligencia de la Armada de Chile, DIRINTA)
        \end{itemize}

\end{itemize}



