\section{Scientific Computing and Applied Mathematics}
%Research description here
Our interest in Scientific Computing and Applied Mathematics is
mainly connected with the use of numerical computation to
solve interesting problems. Our expertise goes from
Mathematical Modeling (\cite{Emelianenko2014,Li2011,Li2010,Torres2010}) to High Performance Computing 
(\cite{Emelianenko2014,Torres2012,Torres2009}).

To name a few particular problems and topics:

\begin{itemize}
 \item Construction of highly parallel preconditioners for solving ill-conditioned linear systems of equations.
      This has been applied in Radial Basis Function interpolation \cite{Torres2009} and Computational Fluid Dynamics
      \cite{Torres2012}.
 \item Translation of an Ant-Based algorithm into a Nonlinear-Stochastic-Dynamical-System for the
  study of parameter dependence \cite{Torres2010} and bifurcation analysis.
  We have also worked in the analysis of a Slime-Mold based model for the construction of
  ad-hoc computer network protocols \cite{Li2011,Li2010} from numerical algorithms.
 \item In partial differential equations (PDE) we have worked with Navier-Stokes equations for
  droplets interactions in a tropical cloud \cite{Torres2012}, this has been a theoretical
  and a numerical analysis. 
  It is important to highlight that our interest in numerical solution of PDE 
  is with the use of mesh and meshless methods,
  specifically meshless methods based on Radial Basis Functions and Vortex methods.
 \item Analysis of 2D grain growth model for polycrystalline materials \cite{Emelianenko2014}.
 This has been an theoretical and numerical analysis as well.
 \item We also have experience with the use of the Shallow Water Equations for the 
 numerical simulations of Tsunamis on the Chilean cost.
\end{itemize}

Finally, we may say we are interested in any great problem that can be modeled Mathematically.

%Some references
\subsection{Publications}

Some publications made in this area
are:\cite{Emelianenko2014},\cite{Torres2012},\cite{Wang2011L},\cite{Li2011},\cite{Li2010},
\cite{Torres2010},\cite{Torres2009}

